---
title: "Debugging the shiny functons"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
vignette: >
  %\VignetteIndexEntry{Debugging the shiny functons}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r pkgs, message=FALSE, warning=FALSE}
library(dbap)
library(dplyr)
library(Lahman)
library(NHANES)
library(palmerpenguins)
```

# Overview 

The output in `dbap` is built by combining the `mod_pkg_data` and `mod_select_vars` modules, which are described below: 

## `mod_pkg_data`

`mod_pkg_data` uses the `get_pkgs_with_dfs()` and functions to populate the first `selectInput()` in the `sidebarPanel()`:

```{r get_pkgs_with_dfs}
# get packages with data.frames/tibbles
pkgs <- get_pkgs_with_dfs()
pkgs
 
```

The `input$pkg` is passed `get_pkg_df_names()` to list the datasets as `input$data`:

```{r get_pkg_df_names}
# select package with data.frames/tibbles
pkg <- pkgs['dplyr']
pkg
get_pkg_df_names(pkg = pkg)
```

The package (`pkg`) and dataset (`pkg_ds`) are passed into `get()` to retrieve the reactive `pkg_data()`:

```{r}
pkg_ds <- get_pkg_df_names(pkg = pkg)[4] # pull starwars data
pkg_data <- base::get(x = pkg_ds, 
                      pos = paste0("package:", pkg))
dplyr::glimpse(pkg_data)
```

## `mod_select_vars`

The `mod_select_vars` has two `selectInput()`s: the first is for the column type function (created with `pull_type_cols()`).  

```{r filtererd}
filtererd <- pull_type_cols(
  data = pkg_data, 
  filter = "is.list")
filtererd
```

The second `selectInput()` displays the column names returned *by* the column type function:

```{r}
dplyr::glimpse(pkg_data[filtererd[1:2]])
```

The `filtererd` vector is used to populate the `selectizeInput()` with the list of column names passed to `df_skim()`:

```{r}
df_skim(pkg_data[filtererd[1:2]])
```

