---
title: "Packages and data.frames"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
vignette: >
  %\VignetteIndexEntry{Packages and data.frames}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = TRUE
)
```

```{r pkgs}
library(dbap)
```

There are multiple helper functions for dealing with packages and data in `dbap`.

# Packages

## `search_list_pkg_nms()`

`search_list_pkg_nms()` returns the names of the packages on the search list:

```{r search_list_pkg_nms}
search_list_pkg_nms()
```

I'll use `grep()` to check to see if a package (`fs`) is installed on the `search()` list:

```{r}
grep(pattern = "package:fs", x = search(), value = TRUE)
```

I can use `loadedNamespaces()` to check for a package in loaded namespaces:

```{r}
"fs" %in% loadedNamespaces()
```

## `check_pkg_ns()`

`check_pkg_ns()` adds a package namespace to `loadedNamespaces()`, but doesn't add it to the search list:

```{r}
# remove package
unloadNamespace("fs")
# check loadedNamespaces
"fs" %in% loadedNamespaces()
# check search list
grep(pattern = "package:fs", x = search(), value = TRUE)
```

Add package namespace:

```{r}
check_pkg_ns("fs")
```

Now check if the package namespace is loaded and on the `search()` list:

```{r}
"fs" %in% loadedNamespaces()
```

```{r}
grep(pattern = "package:fs", x = search(), value = TRUE)
```

## `check_pkg_inst()`

`check_pkg_inst()` will install and load the package namespace:

```{r}
# remove from loaded namespaces
unloadNamespace("fs")
# confirm
"fs" %in% loadedNamespaces()
```

```{r}
check_pkg_inst("fs")
```

This package's namespace is loaded, and it's not on the `search()` list:

```{r}
grep(pattern = "package:fs", x = search(), value = TRUE)
"fs" %in% loadedNamespaces()
```

# Package `data.frame`s

These functions deal with packages containing `data.frame`s.

## `get_pkgs_with_dataframes()`

```{r pkg_nms_with_data_frames, message=FALSE, warning=FALSE}
check_pkg_inst(c("dplyr", "tidyr", "forcats", "lubridate"))
check_pkg_ns(c("dplyr", "tidyr", "forcats", "lubridate"))
pkg_nms_with_data_frames()
```

## `pkg_data_frame_nms()`

`pkg_data_frame_nms()` returns the names of the `data.frame` data objects:

```{r pkg_data_frame_nms, message=FALSE, warning=FALSE}
pkg_data_frame_nms(pkg = "lubridate")
```

If there are no `data.frame`s, `NULL` is returned:

```{r pkg_data_frame_nms-null, message=FALSE, warning=FALSE}
pkg_data_frame_nms(pkg = "fs")
```

## `pkg_data_object()`

`pkg_data_object()` is a wrapper around `get()` and returns the data object from a package:

```{r pkg_data_object}
str(pkg_data_object(ds = "storms", pkg = "dplyr"))
```

```{r}
str(pkg_data_object(ds = "Theoph", pkg = "datasets"))
```

## `pkg_data_results()`

`pkg_data_results()` returns the `results` from `data(package = pkg)`

```{r}
pkg_data_results(pkg = c("forcats", "lubridate"))
```

If `pkg` doesn't have any data objects, it returns an empty tibble.

```{r}
pkg_data_results(pkg = "fs")
```

## `pkg_data_str()`

`pkg_data_str()` returns the 'package data structure' tibble, which contains the `Package`, `Item`, Title, Class, total Columns and Rows, and column counts by type (`Logical`, `Numeric`, `Character`, `Factor`, `List`)

```{r}
pkg_data_str(pkg = "dplyr")
```


```{r}
pkg_data_str(pkg = c("forcats", "lubridate"))
```
