---
title: "Packages and data.frames"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
vignette: >
  %\VignetteIndexEntry{Packages and data.frames}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = TRUE
)
```

```{r pkgs}
library(dbap)
```

There are multiple helper functions for dealing with packages and data in `dbap`. 

# Packages 

## `search_list_pkg_nms()`

```{r search_list_pkg_nms}
search_list_pkg_nms()
```


Check to see if a package (`fs`) is installed on the `search()` list:

```{r}
grep(pattern = "package:fs", x = search(), value = TRUE)
```

Check for package in loaded namespaces: 

```{r}
"fs" %in% loadedNamespaces()
```

## `check_pkg_ns()`

`check_pkg_ns()` will add the package namespace to `loadedNamespaces()`, but not add it to the search list: 

```{r}
# remove package
unloadNamespace("fs")
# check search list
grep(pattern = "package:fs", x = search(), value = TRUE)
# check loadedNamespaces
"fs" %in% loadedNamespaces()
```

Add package namespace: 

```{r}
check_pkg_ns("fs")
```

Now check if the package namespace is loaded and on the `search()` list: 

```{r}
"fs" %in% loadedNamespaces()
```


```{r}
grep(pattern = "package:fs", x = search(), value = TRUE)
```

## `check_pkg_inst()`

`check_pkg_inst()` will install and load the package namespace:

```{r}
# remove from loaded namespaces
unloadNamespace("fs")
# confirm
"fs" %in% loadedNamespaces()
```


```{r}
check_pkg_inst("fs")
```

This package's namespace is loaded, and it's not on the `search()` list: 

```{r}
grep(pattern = "package:fs", x = search(), value = TRUE)
"fs" %in% loadedNamespaces()
```

# Package `data.frame`s

These functions deal with packages containing `data.frame`s.

## `get_pkgs_with_dataframes()`

```{r pkg_nms_with_data_frames, message=FALSE, warning=FALSE}
check_pkg_inst(c("dplyr", "tidyr", "forcats", "lubridate"))
check_pkg_ns(c("dplyr", "tidyr", "forcats", "lubridate"))
pkg_nms_with_data_frames()
```


## `pkg_data_frame_nms()`

`pkg_data_frame_nms()` returns the names of the `data.frame` data objects:

```{r pkg_data_frame_nms, message=FALSE, warning=FALSE}
pkg_data_frame_nms(pkg = "lubridate")
```

If there are no `data.frame`s, `NULL` is returned: 

```{r pkg_data_frame_nms-null, message=FALSE, warning=FALSE}
pkg_data_frame_nms(pkg = "fs")
```

## `pkg_data_object()`

```{r pkg_data_object}
str(pkg_data_object(ds = "storms", pkg = "dplyr"))
```

## `pkg_data_results()`

```{r}
pkg_data_results(pkg = c("forcats", "lubridate"))
```

## `pkg_data_str()`

```{r}
pkg_data_str(pkg = c("forcats", "lubridate"))
```
